Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems

### 2017-08-02 LaTeX/Turnover.tex
position figure updated

	\node[] () {\includegraphics[width=\linewidth]{PositionPlot_2}};
	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
%	\node[anchor=east] at (6.5, -3) {\footnotesize pollen competition (ploidy-antagonism)};%, $s^\female < s^\female$};
	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);

@@

Invasion fitness of a neo-sex-determining allele plotted against the relative genomic location of a locus under direct selection, \textbf{A}, for various selective regimes. 
The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
In A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic \citep[following][]{vanDoorn:2010hu}, in which case a neo-W can only invade if it is more closely linked to the selected locus ($s^\female=1/10$, $h^\female=7/10$ $s^\male=-1/10$, $h^\male=3/10$).
In B-D we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 

@@

In B

>>>>

	\node[] () {\includegraphics[width=0.5\linewidth]{PositionPlot_2}};
%	\node[anchor=east] at (0, 1.5) {\footnotesize diploid sex-antagonism}; %, $s^\male s^\female < 0$};
%	\node[anchor=east] at (6.5, 1.5) {\footnotesize haploid sex-antagonism}; %, $s^\male s^\female > 0$};
%	\node[anchor=east] at (0, -3) {\footnotesize male drive (ploidy-antagonism)}; %, $s^\male < s^\female$};
%	\node[anchor=east] at (6.5, -3) {\footnotesize find something interesting to plot};%, $s^\female < s^\female$};
%	\node[anchor=center] at (-1.3, 4.25) {\scriptsize tighter sex-linkage};
%	\node[anchor=center] at (2.45, 3.5) {\scriptsize ancestral SDR};
%	\draw[->,thick] (2.45, 3.25) -- (2.45, 2.5);
%	\node[anchor=center] at (-1.4, -0.25) {\scriptsize novel SDR};
%	\draw[->,thick] (-1.4, -0.5) -- (-1.4, -1);

@@

Invasion fitness of a neo-sex-determining allele plotted against the relative genomic location of a locus under direct selection for various selective regimes. 
% (neo-Y invading ZW in black, neo-W invading XY in red)
%The ancestral sex-determining locus is located at -25 and the novel sex-determining locus is located at 25. %and that there is a polymorphism at the \textbf{A} locus maintained by selection.
%Thus, if the neo-sex-determining allele invades in the gray region the system evolves tighter sex-linkage.  
We use Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans, cM) to the probability of a cross-over event. 
In panel A, there is no haploid selection ($t^\Hermaphrodite=\alpha^\Hermaphrodite_{\Delta}=0$) and selection in diploids is sexually antagonistic ($s^\male=-s^\female=1/10$, $h^\male=1-h^\female=3/10$), in which case the neo-sex-determining allele can only invade if it is more closely linked to the selected locus ($R<r$; gray region).
In panel B, there is no diploid selection ($s^\Hermaphrodite=0$) and selection in haploids is sexually antagonistic ($t^\male=-t^\female=0.08$, $\alpha^\Hermaphrodite_{\Delta}=0$), in which case the neo-sex-determining allele can invade regardless of linkage.   
In panel C, selection in diploids ($s^\male=s^\female=1/10$, $h^\male=h^\female=7/10$) opposes drive in males ($\alpha^\male_{\Delta}=-0.05$, $t^\Hermaphrodite=\alpha^\female_{\Delta}=0$), in which case the neo-sex-determining allele can once again invade regardless of linkage.   
%we include haploid selection. %and assume that selection in diploids is not sexually-antagonistic ($s^\female s^\male>0$). 

@@
